An introduction to wavelets using R

### 2022-01-13 text/14/wavelets.Rmd
Added reference to wavelets.Rmd
Added second reference to wavelets.Rmd

@@

In one dimention, the d8 wavelet looks like this.

@@

>>>>

The best explanation of the inverse wavelet transformation is a [page][kap1] buried deep in Ian Kaplan's website, bearcave. Also helpful is this [pdf file][nar1] of Chapter 2 of a book on wavelets.

@@

In one dimension, the d8 wavelet looks like this.

@@

[kap1]: http://bearcave.com/software/java/wavelets/daubechies/index.html
[nar1]: http://dsp-book.narod.ru/PWSA/8276_02.pdf
